\bf An Examination of Sport Climbing Competition Format and Scoring System

### 2021-08-02 manuscript/Rmd/draft.Rmd
Paper abstract

keywords:
- sport climbing
- scoring system
- 2020 Summer Olympics

abstract: |
  The purpose of this paper is to investigate sport climbing, one of the sports making its debut on the Olympics stage at Tokyo 2020. In particular, we take a closer look at the controversial competition format and scoring system of sport climbing... Simulation. Data Analysis: drop and re-rank, correlations
bibliography: references.bib
output: rticles::asa_article
---

@@

The decision to combine the three climbing events and only award one set of medals for both men's and women's events in the Olympics has received a large amount of criticism from climbing athletes all over the world (CITATION NEEDED). In a series of interviews conducted by Climbing Magazine in 2016, a number of climbers shared their thoughts and concerns about the new Olympics climbing format. Climber Lynn Hill compared the idea of combining speed climbing, bouldering, and lead climbing to "asking a middle distance runner to compete in the sprint" (CITATION NEEDED). She then added "Speed climbing is a sport within our sport". Other climbers also hold the same opinion as Hill regarding speed climbing, using words and phrases like "bogus", "a bummer", "less than ideal", "not in support", and "cheesy and unfair" to describe the new combined competition format. Courtney Woods stated "Speed climbers will have the biggest disadvantage because their realm isn’t based on difficult movements". Mike Doyle believed "Honestly, the people that will suffer the most are the ones that focus only on speed climbing. Those skills/abilities don’t transfer as well to the other disciplines". Most climbers also expressed their hope for a change in the format in future tournaments, with some calling for each discipline to have its own set of medals. See @blanchard2016 for more information on these interviews.

>>>>

keywords:
- sport climbing
- rankings
- 2020 Summer Olympics

abstract: |
  The purpose of this paper is to investigate the controversial competition format and scoring system of sport climbing, which is one of the sports making its debut on the Olympics stage at Tokyo 2020. Climbing Olympians will participate in three disciplines (speed climbing, bouldering, and lead climbing) for a single set of medals, and a multiplied score of climbers' rankings in all three disciplines will be used to determine the overall standings. This work finds great evidence from historical data and simulations that speed climbing speed climbing should be separated from the combined format and have its own medals. Furthermore, it is shown that the product of ranks scoring system violates the independence of irrelevant alternatives property.

bibliography: references.bib
output: rticles::asa_article
---

@@

The decision to combine the three climbing events and only award one set of medals for both men's and women's events in the Olympics has received a large amount of criticism from climbing athletes all over the world (CITATION NEEDED - I mentioned the article at the end of the paragrah). In a series of interviews conducted by Climbing Magazine in 2016, a number of climbers shared their thoughts and concerns about the new Olympics climbing format. Climber Lynn Hill compared the idea of combining speed climbing, bouldering, and lead climbing to "asking a middle distance runner to compete in the sprint" (CITATION NEEDED). She then added "Speed climbing is a sport within our sport". Other climbers also hold the same opinion as Hill regarding speed climbing, using words and phrases like "bogus", "a bummer", "less than ideal", "not in support", and "cheesy and unfair" to describe the new combined competition format. Courtney Woods stated "Speed climbers will have the biggest disadvantage because their realm isn’t based on difficult movements". Mike Doyle believed "Honestly, the people that will suffer the most are the ones that focus only on speed climbing. Those skills/abilities don’t transfer as well to the other disciplines". Most climbers also expressed their hope for a change in the format in future tournaments, with some calling for each discipline to have its own set of medals. See @blanchard2016 for more information on these interviews.

### 2021-08-02 manuscript/Rmd/draft.tex
Paper abstract

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{textcomp}
\usepackage[hyphens]{url} % not crucial - just used below for the URL
\usepackage{hyperref}
\usepackage{caption}
\captionsetup[figure]{skip=3pt}
\usepackage{float}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

\bigskip
\begin{abstract}
The purpose of this paper is to investigate sport climbing, one of the
sports making its debut on the Olympics stage at Tokyo 2020. In
particular, we take a closer look at the controversial competition
format and scoring system of sport climbing\ldots{} Simulation. Data
Analysis: drop and re-rank, correlations
\end{abstract}

\noindent%
{\it Keywords:} sport climbing, scoring system, 2020 Summer Olympics
\vfill

@@

The decision to combine the three climbing events and only award one set
of medals for both men's and women's events in the Olympics has received
a large amount of criticism from climbing athletes all over the world
(CITATION NEEDED). In a series of interviews conducted by Climbing
Magazine in 2016, a number of climbers shared their thoughts and
concerns about the new Olympics climbing format. Climber Lynn Hill
compared the idea of combining speed climbing, bouldering, and lead
climbing to ``asking a middle distance runner to compete in the sprint''
(CITATION NEEDED). She then added ``Speed climbing is a sport within our
sport''. Other climbers also hold the same opinion as Hill regarding
speed climbing, using words and phrases like ``bogus'', ``a bummer'',
``less than ideal'', ``not in support'', and ``cheesy and unfair'' to
describe the new combined competition format. Courtney Woods stated
``Speed climbers will have the biggest disadvantage because their realm
isn't based on difficult movements''. Mike Doyle believed ``Honestly,
the people that will suffer the most are the ones that focus only on
speed climbing. Those skills/abilities don't transfer as well to the
other disciplines''. Most climbers also expressed their hope for a
change in the format in future tournaments, with some calling for each
discipline to have its own set of medals. See \citet{blanchard2016} for
more information on these interviews.

@@

\begin{figure}[H]

@@

@@

\newpage

\newpage

>>>>

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{textcomp}
\usepackage[hyphens]{url} % not crucial - just used below for the URL
\usepackage{hyperref}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

\bigskip
\begin{abstract}
The purpose of this paper is to investigate the controversial
competition format and scoring system of sport climbing, which is one of
the sports making its debut on the Olympics stage at Tokyo 2020.
Climbing Olympians will participate in three disciplines (speed
climbing, bouldering, and lead climbing) for a single set of medals, and
a multiplied score of climbers' rankings in all three disciplines will
be used to determine the overall standings. This work finds great
evidence from historical data and simulations that speed climbing speed
climbing should be separated from the combined format and have its own
medals. Furthermore, it is shown that the product of ranks scoring
system violates the independence of irrelevant alternatives property.
\end{abstract}

\noindent%
{\it Keywords:} sport climbing, rankings, 2020 Summer Olympics
\vfill

@@

The decision to combine the three climbing events and only award one set
of medals for both men's and women's events in the Olympics has received
a large amount of criticism from climbing athletes all over the world
(CITATION NEEDED - I mentioned the article at the end of the paragrah).
In a series of interviews conducted by Climbing Magazine in 2016, a
number of climbers shared their thoughts and concerns about the new
Olympics climbing format. Climber Lynn Hill compared the idea of
combining speed climbing, bouldering, and lead climbing to ``asking a
middle distance runner to compete in the sprint'' (CITATION NEEDED). She
then added ``Speed climbing is a sport within our sport''. Other
climbers also hold the same opinion as Hill regarding speed climbing,
using words and phrases like ``bogus'', ``a bummer'', ``less than
ideal'', ``not in support'', and ``cheesy and unfair'' to describe the
new combined competition format. Courtney Woods stated ``Speed climbers
will have the biggest disadvantage because their realm isn't based on
difficult movements''. Mike Doyle believed ``Honestly, the people that
will suffer the most are the ones that focus only on speed climbing.
Those skills/abilities don't transfer as well to the other
disciplines''. Most climbers also expressed their hope for a change in
the format in future tournaments, with some calling for each discipline
to have its own set of medals. See \citet{blanchard2016} for more
information on these interviews.

@@

\begin{figure}

@@

\begin{table}

@@
